Software Architectures for Integrating Workflow Engines in Science Gateways

### 2016-05-13 paper.tex
up to integration complexity

@@

The architectures described in Section~\ref{sec:architectures} are
evaluated in Table~\ref{table:evaluation} using 5 main criteria:
integration complexity, robustness, extensibility, scalability and
other specific features. Criteria break down to specific metrics where
\emph{lower value indicates better performance}. For each criterion, a
global score is computed by summing up the individual metrics. We
ensure that the different metrics in a criterion measure similar
entities so that they can be summed. The criteria and metrics are
explained hereafter.

@@

\emph{Integration complexity} is obtained by counting the total number of
interactions and components on the architecture diagram. It breaks
down to the following 2 metrics:
\begin{itemize}[leftmargin=0cm,itemindent=0.35cm,itemsep=0cm]
\item Total number of components (\texttt{I$_1$}), and
\item Total number of interactions (\texttt{I$_2$}).
\end{itemize}
One may wonder whether infrastructure should be counted in
\texttt{I$_1$} since it is usually not developed by the groups who
integrate workflow engines in science gateway. However, integrating an
infrastructure in the architecture usually requires some technical
effort (e.g., account creation, software installation, APIs, etc.), which is
why we keep it in the metric. The two metrics are summed to obtain a
global score that measures the
total number of software pieces to develop, including interactions and
components.

>>>>

\label{sec:intro_sg}

@@

The architectures described in Section~\ref{sec:architectures} are
evaluated in Table~\ref{table:evaluation} using five main criteria:
integration complexity, robustness, extensibility, scalability and
other specific features. These are based on science gateway properties introduced in Section~\ref{sec:intro_sg}. Criteria break down to specific metrics where
\emph{lower value indicates better performance}. For each criterion, a
global score is computed by summing up the individual scores for each metric. We
ensure that the different metrics used to calculate the global score for a criterion are comparable, so that they can be combined meaningfully. The criteria and metrics are
explained hereafter.

\note{Sil}{is any normalization used, for example, to the maximum values found in the analysis?}

@@

Science gateway \emph{integration complexity} is measured through the number of software components and their interactions. It breaks
down to the following 2 metrics:
\begin{itemize}[leftmargin=0cm,itemindent=0.35cm,itemsep=0cm]
\item Total number of components (\texttt{I$_1$}), and
\item Total number of interactions (\texttt{I$_2$}).
\end{itemize}
One may wonder whether infrastructure should be counted in
\texttt{I$_1$}, since it is usually an external entity that is not developed nor maintained by the groups who
integrate workflow engines in science gateway. We support its inclusion here because integrating an
infrastructure into the system usually requires some technical
effort (e.g., account creation, software installation, APIs, etc.), therefore increasing complexity. The two metrics are summed to obtain a
global score that measures the
total number of software pieces affected by integration.
